Results

### 2019-02-27 02_analysis.Rmd
Fancy tables!

```{r plot-likely-diffs, warning=FALSE, fig.width=6, fig.height=8}
tidied_diffs_likely <- all_models_likely %>% 
  unnest(posterior_chains_long) %>% 
  filter(.variable == "theta_diff") %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  )) %>% 
  mutate(title = str_remove(title, " \\| Crackdown"))

@@

plot_diff_likely_a <- ggplot(level1_likely, aes(x = .value, y = fct_rev(title), fill = title)) +
  geom_halfeyeh(.width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  scale_fill_manual(values = ngo_cols(c("blue", "red", "orange"), name = FALSE), guide = FALSE) +
  labs(x = "Difference in donation likelihood", y = NULL, tag = "A") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_likely_b <- ggplot(filter(level2_likely, condition == "Issue"), 
                             aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("red", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = NULL, y = NULL, tag = "B") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

plot_diff_likely_c <- ggplot(filter(level2_likely, condition == "Funding"), 
                             aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("orange", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "Difference in donation likelihood", y = NULL, tag = "C") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_likely_d <- ggplot(level3_likely, aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("green", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "Difference in donation likelihood", y = NULL, tag = "D",
       caption = "Point shows posterior median; thick black lines show 80% credible interval; thin black lines show 95% credible interval") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

@@

plot_diffs_likely_all %T>% 
  ggsave(., filename = here("output", "figures", "likely-diffs.pdf"),
         width = 6, height = 8, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = here("output", "figures", "likely-diffs.png"),
         width = 6, height = 8, units = "in", type = "cairo", dpi = 300)
```

```{r tbl-likely-diffs-level1, warning=FALSE, message=FALSE, results="asis"}
tbl_likely_tidy <- all_models_likely %>% 
  unnest(tidy) %>% 
  filter(term %in% c("theta_1", "theta_2", "theta_diff", "pct_change")) %>% 
  select(title, term, estimate) %>% 
  spread(term, estimate) %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  ))

@@

tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 1") %>%
  mutate(title = recode(title, 
                        Crackdown = "Crackdown −\nNo crackdown",
                        Issue = "Humanitarian\nassistance −\nHuman rights",
                        Funding = "Private −\nGovernment\nfunding")) %>% 
  mutate(title = fct_inorder(title)) %>% 
  select(`Frame` = title, `% likely~Treatment~` = theta_2, `% likely~Control~` = theta_1,
         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(caption = 'Difference between likelihood of donation across single conditions; values represent posterior medians {#tbl:likely-diffs-1}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-likely-diffs-1.md"))
```

```{r tbl-likely-diffs-level2, warning=FALSE, message=FALSE, results="asis"}
tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 2") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  mutate(title_clean = case_when(
    title_clean %in% c("Human rights", "Humanitarian assistance") ~ paste(title_clean, "issues"),
    title_clean %in% c("Government", "Private") ~ paste(title_clean, "funding")
  )) %>% 
  mutate(title_clean = factor(title_clean, 
                              levels = c("Human rights issues", 
                                         "Humanitarian assistance issues", 
                                         "Government funding", "Private funding"))) %>% 
  arrange(title_clean) %>% 
  select(Frame = title_clean, `% likely~Crackdown~` = theta_2, `% likely~No\\ crackdown~` = theta_1,
         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(caption = 'Difference between likelihood of donation in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:likely-diffs-2}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-likely-diffs-2.md"))
```

```{r tbl-likely-diffs-level3, warning=FALSE, message=FALSE, results="asis"}
tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 3") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  separate(title_clean, c("Issue", "Funding"), sep = " \\| ") %>% 
  mutate(Issue = factor(Issue, levels = c("Human rights", "Humanitarian assistance")),
         Funding = factor(Funding, levels = c("Government", "Private"))) %>% 
  arrange(Issue, Funding) %>% 
  select(`Issue frame` = Issue, `Funding frame` = Funding, 
         `% likely~Crackdown~` = theta_2, `% likely~No\\ crackdown~` = theta_1,
         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(caption = 'Difference between likelihood of donation in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:likely-diffs-3}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-likely-diffs-3.md"))
```

@@

```{r plot-amount-diffs, warning=FALSE, fig.width=6, fig.height=8}
# This will generate a warning because unnest() puts the crackdown values into
# one column and we cheated by renaming issue and funding as crackdown, so it
# gets mad when combining the factors in crackdown with those in issue and
# funding. But because we only care about the diffs, we don't actually need the
# category labels here, so it's all good.
tidied_diffs_amount <- all_models_amount %>% 
  unnest(posterior_chains_long) %>% 
  filter(.variable == "mu_diff") %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  )) %>% 
  mutate(title = str_remove(title, " \\| Crackdown"))

@@

plot_diff_amount_a <- ggplot(level1_amount, aes(x = .value, y = fct_rev(title), fill = title)) +
  geom_vline(xintercept = 0) +
  geom_halfeyeh(.width = c(0.8, 0.95)) +
  scale_x_continuous(labels = dollar) +
  scale_fill_manual(values = ngo_cols(c("blue", "red", "orange"), name = FALSE), guide = FALSE) +
  labs(x = "Difference in amount donated", y = NULL, tag = "A") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_amount_b <- ggplot(filter(level2_amount, condition == "Issue"), 
                             aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("red", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = dollar) +
  labs(x = NULL, y = NULL, tag = "B") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

plot_diff_amount_c <- ggplot(filter(level2_amount, condition == "Funding"), 
                             aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("orange", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = dollar) +
  labs(x = "Difference in amount donated", y = NULL, tag = "C") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_amount_d <- ggplot(level3_amount, aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("green", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = dollar) +
  labs(x = "Difference in amount donated", y = NULL, tag = "D",
       caption = "Point shows posterior median; thick black lines show 80% credible interval; thin black lines show 95% credible interval") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

@@

plot_diffs_amounts_all %T>% 
  ggsave(., filename = here("output", "figures", "amount-diffs.pdf"),
         width = 6, height = 8, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = here("output", "figures", "amount-diffs.png"),
         width = 6, height = 8, units = "in", type = "cairo", dpi = 300)
```

```{r tbl-amount-diffs-level1, warning=FALSE, message=FALSE, results="asis"}
tbl_amounts_tidy <- all_models_amount %>% 
  unnest(tidy) %>% 
  filter(term %in% c("mu", "mu_diff", "pct_change")) %>% 
  group_by(title) %>% 
  mutate(group_id = 1:n()) %>% 
  mutate(term = case_when(
    term == "mu" ~ paste0(term, "_", group_id),
    TRUE ~ term
  )) %>% 
  select(title, term, estimate) %>% 
  spread(term, estimate) %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  )) %>% 
  ungroup()

@@

tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 1") %>%
  mutate(title = recode(title, 
                        Crackdown = "Crackdown −\nNo crackdown",
                        Issue = "Humanitarian\nassistance −\nHuman rights",
                        Funding = "Private −\nGovernment\nfunding")) %>% 
  mutate(title = fct_inorder(title)) %>% 
  select(`Frame` = title, `Amount~treatment~` = mu_2, `Amount~control~` = mu_1,
         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(caption = 'Difference between amount donated across single conditions; values represent posterior medians {#tbl:amount-diffs-1}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-amount-diffs-1.md"))
```

```{r tbl-amount-diffs-level2, warning=FALSE, message=FALSE, results="asis"}
tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 2") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  mutate(title_clean = case_when(
    title_clean %in% c("Human rights", "Humanitarian assistance") ~ paste(title_clean, "issues"),
    title_clean %in% c("Government", "Private") ~ paste(title_clean, "funding")
  )) %>% 
  mutate(title_clean = factor(title_clean, 
                              levels = c("Human rights issues", 
                                         "Humanitarian assistance issues", 
                                         "Government funding", "Private funding"))) %>% 
  arrange(title_clean) %>% 
  select(Frame = title_clean, `Amount~Crackdown~` = mu_2, `Amount~No\\ crackdown~` = mu_1,
         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(caption = 'Difference between amount donated in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:amount-diffs-2}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-amount-diffs-2.md"))
```

```{r tbl-amount-diffs-level3, warning=FALSE, message=FALSE, results="asis"}
tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 3") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  separate(title_clean, c("Issue", "Funding"), sep = " \\| ") %>% 
  mutate(Issue = factor(Issue, levels = c("Human rights", "Humanitarian assistance")),
         Funding = factor(Funding, levels = c("Government", "Private"))) %>% 
  arrange(Issue, Funding) %>% 
  select(`Issue frame` = Issue, `Funding frame` = Funding, 
         `Amount~Crackdown~` = mu_2, `Amount~No\\ crackdown~` = mu_1,
         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(caption = 'Difference between amount donated in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:amount-diffs-3}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-amount-diffs-3.md"))
```

>>>>

```{r plot-likely-diffs, warning=FALSE, fig.width=4.5, fig.height=6.5}
tidied_diffs_likely <- all_models_likely %>% 
  unnest(posterior_chains_long) %>% 
  filter(.variable == "theta_diff") %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  )) %>% 
  mutate(title = str_remove(title, " \\| Crackdown"))

@@

plot_diff_likely_a <- ggplot(level1_likely, aes(x = .value, y = fct_rev(title), fill = title)) +
  geom_halfeyeh(.width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  scale_fill_manual(values = ngo_cols(c("blue", "red", "orange"), name = FALSE), guide = FALSE) +
  labs(x = "Difference in donation likelihood", y = NULL, tag = "A") +
  theme_ngos(base_size = 9) +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_likely_b <- ggplot(filter(level2_likely, condition == "Issue"), 
                             aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("red", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = NULL, y = NULL, tag = "B") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos(base_size = 9) +
  theme(panel.grid.major.y = element_blank())

plot_diff_likely_c <- ggplot(filter(level2_likely, condition == "Funding"), 
                             aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("orange", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "Difference in donation likelihood", y = NULL, tag = "C") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos(base_size = 9) +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_likely_d <- ggplot(level3_likely, aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("green", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "Difference in donation likelihood", y = NULL, tag = "D",
       caption = "Point shows posterior median; thick black lines show 80% credible interval;\nthin black lines show 95% credible interval") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos(base_size = 9) +
  theme(panel.grid.major.y = element_blank())

@@

plot_diffs_likely_all %T>% 
  ggsave(., filename = here("output", "figures", "likely-diffs.pdf"),
         width = 4.5, height = 6.5, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = here("output", "figures", "likely-diffs.png"),
         width = 4.5, height = 6.5, units = "in", type = "cairo", dpi = 300)
```

```{r tbl-likely-diffs-level1, warning=FALSE, message=FALSE}
tbl_likely_tidy <- all_models_likely %>% 
  unnest(tidy) %>% 
  filter(term %in% c("theta_1", "theta_2", "theta_diff", "pct_change")) %>% 
  select(title, term, estimate) %>% 
  spread(term, estimate) %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  ))

@@

tbl_likely_1 <- tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 1") %>%
  mutate(title = recode(title, 
                        Crackdown = "Crackdown − No crackdown",
                        Issue = "*Humanitarian assistance − Human rights*",
                        Funding = "*Private − Government funding*")) %>% 
  mutate_at(vars(theta_1, theta_2, theta_diff, pct_change), 
            funs(percent_format(accuracy = 0.1)(.))) %>% 
  mutate(p.diff.not0 = as.character(round(p.diff.not0, 2))) %>%
  select(Frame = title, `% likely~Treatment~` = theta_2, `% likely~Control~` = theta_1,
         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
```

```{r tbl-likely-diffs-level2, warning=FALSE, message=FALSE}
tbl_likely_2 <- tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 2") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  mutate(title_clean = case_when(
    title_clean %in% c("Human rights", "Humanitarian assistance") ~ paste(title_clean, "issues"),
    title_clean %in% c("Government", "Private") ~ paste(title_clean, "funding")
  )) %>% 
  mutate(title_clean = factor(title_clean, 
                              levels = c("Human rights issues", 
                                         "Humanitarian assistance issues", 
                                         "Government funding", "Private funding"))) %>% 
  arrange(title_clean) %>% 
  mutate_at(vars(theta_1, theta_2, theta_diff, pct_change), 
            funs(percent_format(accuracy = 0.1)(.))) %>% 
  mutate(p.diff.not0 = as.character(round(p.diff.not0, 2))) %>% 
  mutate(title_clean = as.character(title_clean)) %>% 
  select(`H~2a~ and H~3a~` = title_clean, 
         `% likely~Crackdown~` = theta_2, `% likely~No\\ crackdown~` = theta_1,
         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
```

```{r tbl-likely-diffs-level3, warning=FALSE, message=FALSE}
tbl_likely_3 <- tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 3") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  separate(title_clean, c("Issue", "Funding"), sep = " \\| ") %>% 
  mutate(Issue = factor(Issue, levels = c("Human rights", "Humanitarian assistance")),
         Funding = factor(Funding, levels = c("Government", "Private"))) %>% 
  arrange(Issue, Funding) %>% 
  mutate_at(vars(theta_1, theta_2, theta_diff, pct_change), 
            funs(percent_format(accuracy = 0.1)(.))) %>% 
  mutate(p.diff.not0 = as.character(round(p.diff.not0, 2))) %>%
  mutate(Frame = paste0(Issue, " issues, ", Funding, " funding")) %>% 
  select(`H~2a~ and H~3a~ (nested)` = Frame,
         `% likely~Crackdown~` = theta_2, `% likely~No\\ crackdown~` = theta_1,
         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
```

```{r combine-likely-tables, results="asis"}
tbl_likely_2_header <- enframe(colnames(tbl_likely_2)) %>% 
  mutate(value = pandoc.strong.return(value)) %>% 
  spread(name, value) %>% 
  set_names(colnames(tbl_likely_1))

tbl_likely_3_header <- enframe(colnames(tbl_likely_3)) %>% 
  mutate(value = pandoc.strong.return(value)) %>% 
  spread(name, value) %>% 
  set_names(colnames(tbl_likely_1))

bind_rows(tbl_likely_1, 
          tbl_likely_2_header, 
          set_names(tbl_likely_2, colnames(tbl_likely_1)),
          tbl_likely_3_header,
          set_names(tbl_likely_3, colnames(tbl_likely_1))) %>% 
  rename(`H~1a~` = Frame) %>% 
  pandoc.table.return(caption = 'Likelihood of donation and differences in proportions in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:likely-diffs}',
                      justify = "lccccc") %T>%
  cat() %>%
  cat(file = here("output", "tables", "tbl-likely-diffs.md"))
```

@@

```{r plot-amount-diffs, warning=FALSE, fig.width=4.5, fig.height=6.5}
# This will generate a warning because unnest() puts the crackdown values into
# one column and we cheated by renaming issue and funding as crackdown, so it
# gets mad when combining the factors in crackdown with those in issue and
# funding. But because we only care about the diffs, we don't actually need the
# category labels here, so it's all good.
tidied_diffs_amount <- all_models_amount %>% 
  unnest(posterior_chains_long) %>% 
  filter(.variable == "mu_diff") %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  )) %>% 
  mutate(title = str_remove(title, " \\| Crackdown"))

@@

plot_diff_amount_a <- ggplot(level1_amount, aes(x = .value, y = fct_rev(title), fill = title)) +
  geom_vline(xintercept = 0) +
  geom_halfeyeh(.width = c(0.8, 0.95)) +
  scale_x_continuous(labels = dollar) +
  scale_fill_manual(values = ngo_cols(c("blue", "red", "orange"), name = FALSE), guide = FALSE) +
  labs(x = "Difference in amount donated", y = NULL, tag = "A") +
  theme_ngos(base_size = 9) +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_amount_b <- ggplot(filter(level2_amount, condition == "Issue"), 
                             aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("red", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = dollar) +
  labs(x = NULL, y = NULL, tag = "B") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos(base_size = 9) +
  theme(panel.grid.major.y = element_blank())

plot_diff_amount_c <- ggplot(filter(level2_amount, condition == "Funding"), 
                             aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("orange", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = dollar) +
  labs(x = "Difference in amount donated", y = NULL, tag = "C") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos(base_size = 9) +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_amount_d <- ggplot(level3_amount, aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("green", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = dollar) +
  labs(x = "Difference in amount donated", y = NULL, tag = "D",
       caption = "Point shows posterior median; thick black lines show 80% credible interval;\nthin black lines show 95% credible interval") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos(base_size = 9) +
  theme(panel.grid.major.y = element_blank())

@@

plot_diffs_amounts_all %T>% 
  ggsave(., filename = here("output", "figures", "amount-diffs.pdf"),
         width = 4.5, height = 6.5, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = here("output", "figures", "amount-diffs.png"),
         width = 4.5, height = 6.5, units = "in", type = "cairo", dpi = 300)
```

```{r tbl-amount-diffs-level1, warning=FALSE, message=FALSE}
tbl_amounts_tidy <- all_models_amount %>% 
  unnest(tidy) %>% 
  filter(term %in% c("mu", "mu_diff", "pct_change")) %>% 
  group_by(title) %>% 
  mutate(group_id = 1:n()) %>% 
  mutate(term = case_when(
    term == "mu" ~ paste0(term, "_", group_id),
    TRUE ~ term
  )) %>% 
  select(title, term, estimate) %>% 
  spread(term, estimate) %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  )) %>% 
  ungroup()

@@

tbl_amount_1 <- tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 1") %>%
  mutate(title = recode(title, 
                        Crackdown = "Crackdown − No crackdown",
                        Issue = "*Humanitarian assistance − Human rights*",
                        Funding = "*Private − Government funding*")) %>% 
  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), funs(as.character(round(., 2)))) %>% 
  mutate(pct_change = percent_format(accuracy = 0.1)(pct_change)) %>%
  select(`Frame` = title, `Amount~Treatment~` = mu_2, `Amount~Control~` = mu_1,
         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
```

```{r tbl-amount-diffs-level2, warning=FALSE, message=FALSE}
tbl_amount_2 <- tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 2") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  mutate(title_clean = case_when(
    title_clean %in% c("Human rights", "Humanitarian assistance") ~ paste(title_clean, "issues"),
    title_clean %in% c("Government", "Private") ~ paste(title_clean, "funding")
  )) %>% 
  mutate(title_clean = factor(title_clean, 
                              levels = c("Human rights issues", 
                                         "Humanitarian assistance issues", 
                                         "Government funding", "Private funding"))) %>% 
  arrange(title_clean) %>% 
  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), funs(as.character(round(., 2)))) %>% 
  mutate(pct_change = percent_format(accuracy = 0.1)(pct_change)) %>%
  mutate(title_clean = as.character(title_clean)) %>% 
  select(`H~2b~ and H~3b~` = title_clean, `Amount~Crackdown~` = mu_2, `Amount~No\\ crackdown~` = mu_1,
         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
```

```{r tbl-amount-diffs-level3, warning=FALSE, message=FALSE}
tbl_amount_3 <- tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 3") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  separate(title_clean, c("Issue", "Funding"), sep = " \\| ") %>% 
  mutate(Issue = factor(Issue, levels = c("Human rights", "Humanitarian assistance")),
         Funding = factor(Funding, levels = c("Government", "Private"))) %>% 
  arrange(Issue, Funding) %>% 
  mutate(Frame = paste0(Issue, " issues, ", Funding, " funding")) %>% 
  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), funs(as.character(round(., 2)))) %>% 
  mutate(pct_change = percent_format(accuracy = 0.1)(pct_change)) %>%
  select(`H~2b~ and H~3b~ (nested)` = Frame,
         `Amount~Crackdown~` = mu_2, `Amount~No\\ crackdown~` = mu_1,
         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0)
```

```{r combine-amount-tables, results="asis"}
tbl_amount_2_header <- enframe(colnames(tbl_amount_2)) %>% 
  mutate(value = pandoc.strong.return(value)) %>% 
  spread(name, value) %>% 
  set_names(colnames(tbl_amount_1))

tbl_amount_3_header <- enframe(colnames(tbl_amount_3)) %>% 
  mutate(value = pandoc.strong.return(value)) %>% 
  spread(name, value) %>% 
  set_names(colnames(tbl_amount_1))

bind_rows(tbl_amount_1, 
          tbl_amount_2_header, 
          set_names(tbl_amount_2, colnames(tbl_amount_1)),
          tbl_amount_3_header,
          set_names(tbl_amount_3, colnames(tbl_amount_1))) %>% 
  rename(`H~1b~` = Frame) %>% 
  pandoc.table.return(caption = 'Mean values and differences in means for amount donated in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:amount-diffs}',
                      justify = "lccccc") %T>%
  cat() %>%
  cat(file = here("output", "tables", "tbl-amount-diffs.md"))
```
